---
title: "Validated Multi-Perspectives Visual Features in Imagery with Interpretable Machine Learning for Detecting Rural Vacant Courtyards in North China"
author: "Qiao zehao Xuwenyu"
date: "`r Sys.Date()`"
output:
  tidyfridoc::html_pretty:
    theme: hpstr
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      dpi = 400,
                      warning = FALSE,
                      message = FALSE,
                      out.width = "100%",
                      out.height = "500px",
                      fig.align = 'center',
                      comment = "#>")
```
## Introduction ####
Zehao Qiao: Writing – original draft, Writing – review & editing, Visualization, Validation, Software, Investigation, Methodology, Formal analysis, Data curation. Maojun Wang: Writing – review and editing, Supervision, Project administration, Funding acquisition, Formal analysis, Conceptualization. Xuexia Zhang: Validation, Supervision, Methodology, Funding acquisition. Wenyu Xu: Writing – original draft, Visualization, Investigation, Methodology, Data curation. Juanjuan Zhao: Writing – review & editing, Formal analysis. Xiaojie Zhang: Validation, Investigation, Data curation. Tao Liu: Supervision, Investigation, Funding acquisition, Conceptualization. Guangzhong Cao: Resources, Funding acquisition, Conceptualization.


## 1.load packages ####
```{r}
library(xgboost)
library(shapviz)
library(ggplot2)
library(readxl)
library(tidyverse)
library(Matrix)  
```

## 2.read data ####
## 2.1 divide dataset, TrainingData(700) and TestData(299).
```{r}
dt <- read_excel("features.examples.xlsx")
str(dt)
dt <- as.data.frame(dt)
dt[,2:11] <- lapply(dt[,2:11], factor)

set.seed(0)  
s = sample(999,700)  
TrainingData = dt[s,]  
TestData = dt[-s,]

TrainingData.Y <- TrainingData[,1]
TrainingData.overhead <- TrainingData[,2:6]
TrainingData.horizontal <- TrainingData[,7:11]
TrainingData.final <- TrainingData[,c(2,3:5)]

TestData.Y <- TestData[,1]
TestData.overhead <- TestData[,2:6]
TestData.horizontal <- TestData[,7:11]
TestData.final <- TestData[,c(2,3:5)]
```
## 3 overhead perspective model    ####
```{r}
dtrain.overhead <- xgb.DMatrix(data.matrix(TrainingData.overhead), 
                               label=TrainingData.Y)
dtest.overhead <- xgb.DMatrix(data.matrix(TestData.overhead), 
                               label=TestData.Y)

fit.overhead <- xgb.train(
  params = list(learning_rate = 0.1, objective = "binary:logistic"),
  data = dtrain.overhead,
  nrounds = 65L)

pre_xgb = round(predict(fit.overhead,newdata = dtest.overhead))  
(test.overhead <- table(TestData.Y,pre_xgb,dnn=c("true","pre")))
(Accuracy.test.overhead = sum(diag(test.overhead))/nrow(TestData.overhead))
(Recall.test.overhead = test.overhead[1,1]/(test.overhead[1,1]+
                                              test.overhead[1,2]))
(Precision.test.overhead = test.overhead[1,1]/(test.overhead[1,1]+
                                                 test.overhead[2,1]))
(F1 <- 2*Precision.test.overhead*Recall.test.overhead/(Precision.test.overhead+
                                                         Recall.test.overhead))

shp <- shapviz(fit.overhead, 
               X_pred = data.matrix(TestData.overhead),
               X = TestData.overhead)

sv_importance(shp,show_numbers = TRUE)+
  theme_bw()

sv_importance(shp, kind = "beeswarm")+
  theme_bw()
```

## 4 horizontal perspective model    ####
```{r}
dtrain.horizontal <- xgb.DMatrix(data.matrix(TrainingData.horizontal), 
                                 label=TrainingData.Y)
dtest.horizontal <- xgb.DMatrix(data.matrix(TestData.horizontal), 
                                label=TestData.Y)

fit.horizontal <- xgb.train(
  params = list(learning_rate = 0.1, objective = "binary:logistic"),
  data = dtrain.horizontal,
  nrounds = 65L)

pre_xgb = round(predict(fit.horizontal,newdata = dtest.horizontal))  
(test.horizontal <- table(TestData.Y,pre_xgb,dnn=c("true","pre")))
(Accuracy.test.horizontal = sum(diag(test.horizontal))/nrow(TestData.horizontal))
(Recall.test.horizontal = test.horizontal[1,1]/(test.horizontal[1,1]+
                                                  test.horizontal[1,2]))
(Precision.test.horizontal = test.horizontal[1,1]/(test.horizontal[1,1]+
                                                     test.horizontal[2,1]))
(F1 <- 2*Precision.test.horizontal*Recall.test.horizontal/(Precision.test.horizontal+
                                                             Recall.test.horizontal))

shp <- shapviz(fit.horizontal, 
               X_pred = data.matrix(TestData.horizontal),
               X = TestData.horizontal)

sv_importance(shp,show_numbers = TRUE)+
  theme_bw()

sv_importance(shp, kind = "beeswarm")+
  theme_bw()
```
## 5 final perspective model    ####
```{r}
dtrain.final <- xgb.DMatrix(data.matrix(TrainingData.final), 
                            label=TrainingData.Y)
dtest.final <- xgb.DMatrix(data.matrix(TestData.final), 
                           label=TestData.Y)

fit.final <- xgb.train(
  params = list(learning_rate = 0.1, objective = "binary:logistic"),
  data = dtrain.final,
  nrounds = 65L)

pre_xgb = round(predict(fit.final,newdata = dtest.final))  
(test.final <- table(TestData.Y,pre_xgb,dnn=c("true","pre")))
(Accuracy.test.final = sum(diag(test.final))/nrow(TestData.final))
(Recall.test.final = test.final[1,1]/(test.final[1,1]+
                                        test.final[1,2]))
(Precision.test.final = test.final[1,1]/(test.final[1,1]+
                                           test.final[2,1]))
(F1 <- 2*Precision.test.final*Recall.test.final/(Precision.test.final+
                                                   Recall.test.final))

shp <- shapviz(fit.final, 
               X_pred = data.matrix(TestData.final),
               X = TestData.final)

sv_importance(shp,show_numbers = TRUE)+
  theme_bw()

sv_importance(shp, kind = "beeswarm")+
  theme_bw()
```

---


<h5 align="center">©examples </h5>
